### 2014-02-22 reanalysis/ComBat_original/combat_paper_dataset2_reproduced.rmd
g

This <b>report</b> aims to show to what extent the use of ComBat led to false results in the second "proof of concept" analysis performed in Johnson et al. The example named "Data Set 2" and their analysis are described in the supplementary materials for Johnson et al.
Description on how to obtain the data were found [here](https://groups.google.com/forum/#!msg/combat-user-forum/S9vBcXw8RGk/QIoD6oRBM9IJ) which had links to [dataExample2.txt](http://www.bu.edu/jlab/wp-assets/ComBat/data/dataExample2.txt)
and [sampleInfoExample2.txt](http://www.bu.edu/jlab/wp-assets/ComBat/data/sampleInfoExample2.txt)

@@

>>>>

This <b>report</b> aims to show to what extent the use of ComBat led to false results in the second "proof of concept" analysis performed in Johnson et al. The example named "Data Set 2" and their analysis are described in the [supplementary material](http://biostatistics.oxfordjournals.org/content/suppl/2006/04/21/kxj037.DC1/kxj037supp.pdf) for [Johnson et al.](http://biostatistics.oxfordjournals.org/content/8/1/118.abstract)
Description on how to obtain the data were found [here](https://groups.google.com/forum/#!msg/combat-user-forum/S9vBcXw8RGk/QIoD6oRBM9IJ) which had links to [dataExample2.txt](http://www.bu.edu/jlab/wp-assets/ComBat/data/dataExample2.txt)
and [sampleInfoExample2.txt](http://www.bu.edu/jlab/wp-assets/ComBat/data/sampleInfoExample2.txt)

@@

Johnson, WE, Rabinovic, A, and Li, C (2007). Adjusting batch effects in microarray expression data using Empirical Bayes methods. Biostatistics 8(1):118-127.
